Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Simplify wording in last paragraph

From these results we can make the recommendation that physical model tests
should be on the order $Re_D \sim 10^6$ to provide predictions of full-scale
performance. This threshold also applies to the validation of predictive
engineering models, especially for high-fidelity CFD models where the boundary
layer is to be resolved, since transition to turbulence plays an important role
in overall blade loading. Note that in our case blockage, though reasonably low,
may be increasing flow through the turbine compared with a free case, which
could mean $Re$ thresholds for free flows could be slightly higher, though a
reliable blockage correction algorithm has not yet been agreed upon for CFTs
\cite{Cavagnaro2014}.

>>>>

From these results we recommend that physical model tests be performed at $Re_D
\sim 10^6$ to provide reasonable predictions of full-scale performance. This
threshold also applies to the validation of predictive engineering models,
especially for high-fidelity CFD models where the boundary layer is to be
resolved, since transition to turbulence plays an important role in overall
blade loading. Note that in our case blockage, though reasonably low, may be
increasing flow through the turbine compared with a free case, which could mean
$Re$ thresholds for free flows could be slightly higher, though a reliable
blockage correction algorithm has not yet been agreed upon for CFTs
\cite{Cavagnaro2014}.
